A Method for Regularisation of Evolutionary Polynomial Regressions

### 2013-12-13 texts/submission_02-asc/paper_spfga-review.tex
Updated figures.

\caption{Results for Artificial dataset. As shown, \ac{GAPolyreg} was able to find the exact polynomial structure that generates the dataset, reducing the test set prediction error to zero.  The regression methods depicted are: 1. \ac{GAPolyreg}, 2. Random Forests, 3. Linear Regression, 4. SVM, 5. Regression Trees and 6. Conditional Inference Trees}
\label{artificial_dataset1_lambda1.0}

@@

\caption{Summary results for different regression methods on the Housing, Abalone, Auto MPG and Kinematics datasets. Random Forests, an ensemble method (``2'' in the plots), has the better results. However \ac{GAPoly} achieves similar errors in two of the datasets. For the remaining two \ac{GAPoly} produces similar errors to the other classic regression methods.  The regression methods depicted in these figures are: 1. \ac{GAPoly}, 2. Random Forests, 3. Linear Regression, 4. SVM, 5. Regression Trees and 6. Conditional Inference Trees}
\label{Housing_dataset_lambda0.8_25runs}
\label{Abalone_dataset_lambda0.8_25runs}
\label{Auto-Mpg_dataset_lambda0.8_25runs}
\label{Kinematics300_lambda0.8_25runs}
\end{center}\end{figure*}

@@

Just as an example of the model the \ac{GAPoly} algorithm outputs: in this dataset the best polynomial,

$$y = -0.12 x_6 x_9^4 + 0.78 x_6 - 0.4 x_9^2 x_{13} + 0.17 x_{13}^2 - 0.044$$

where the attributes mean:
$x_6$, RM average number of rooms per dwelling;
$x_9$, RAD index of accessibility to radial highways;
$x_{13}$, Lower status of the population.

For comparison, if we access the mean decrease in accuracy found by Random Forests, the most important attributes are --- in decreasing order --- $x_{13}, x_6, x_5$ (but $x_5$ is already considered $4$ times less important than $x_6$). Both algorithms agree in two of their three most important attributes.

>>>>

\caption{Results for Artificial dataset. As shown, polynomial regression finds the exact polynomial structure that generates the dataset, reducing the test set prediction error to zero.  The regression methods depicted are: 1. \ac{GAPolyreg}, 2. Linear Regression, 3. SVM, 4. Regression Trees and 5. Conditional Inference Trees}
\label{artificial_dataset1_lambda1.0}

@@

\caption{Summary results for different regression methods on the Housing, Abalone, Auto MPG and Kinematics datasets. Random Forests, an ensemble method (``2'' in the plots), has the better results. However \ac{GAPoly} achieves similar errors in two of the datasets. For the remaining two \ac{GAPoly} produces similar errors to the other classic regression methods.  The regression methods depicted in these figures are: 1. \ac{GAPolyreg}, 2. \ac{GAPoly}, 3. Linear Regression, 4. SVM, 5. Regression Trees and 6. Conditional Inference Trees}
\label{Housing_dataset_lambda0.8_25runs}
\label{Abalone_dataset_lambda0.8_25runs}
\label{Auto-Mpg_dataset_lambda0.8_25runs}
\label{Kinematics300_lambda0.8_25runs}
\end{center}\end{figure*}

@@
